Influence of Connectivity on Dung Beetle Communities

### 2025-04-02 corridor_docs/eric_ms_thesis/MS_thesis.Rmd
last beetle weights and partitioning some of paragraph 1 and 2
GLMMs

not_in_all_hab<-btl_sums_patch %>% 
  rename(species=Species) %>% 
  left_join(spp_abund) %>% 
  select(-n,-Guild) %>% 
  filter(m<1|c<1|w<1|r<1)

# This finalizes the table for Table 1
spp_table_data<-btl_sums_patch %>% 
  rename(species=Species) %>% 
  left_join(spp_abund) %>% 
  relocate(n,.after="Guild") %>% 
  mutate(c=case_when(
  c == 0 ~ " ",
  c > 0 ~ "x",
  .default = as.character(c)
)) %>% 
  mutate(m=case_when(
  m == 0 ~ " ",
  m > 0 ~ "x",
  .default = as.character(m)
)) %>% 
  mutate(r=case_when(
  r == 0 ~ " ",
  r > 0 ~ "x",
  .default = as.character(r)
)) %>% 
mutate(w=case_when(
  w == 0 ~ " ",
  w > 0 ~ "x",
  .default = as.character(w)
)) %>% 
  mutate(Guild=case_when(
  Guild == "r" ~ "roll",
  Guild == "t" ~ "tunnell",
  Guild == "d" ~ "dwell",
  .default = as.character(Guild)
)) %>% 
  rename(Species=species,
         N=n,
         Matrix=m,
         Corridor=c,
         Winged=w,
         Rectangular=r)

>>>>

not_in_all_hab<-btl_sums_patch %>% 
  rename(species=Species) %>% 
  left_join(spp_abund) %>% 
  select(-n,-Guild) %>% 
  mutate(row_sums=m+c+r+w) %>% 
  filter(row_sums<4)

# row_sums==1 for any restricted to only one habitat 
# row_sums==2 for any restricted to only two habitats...

# filter(m<1|c<1|w<1|r<1)

# This finalizes the table for Table 1

spp_table_data<-btl_sums_patch %>% 
  rename(species=Species) %>% 
  left_join(spp_abund) %>% 
  relocate(n,.after="Guild") %>% 
  mutate(c=case_when(
  c == 0 ~ " ",
  c > 0 ~ "x",
  .default = as.character(c)
)) %>% 
  mutate(m=case_when(
  m == 0 ~ " ",
  m > 0 ~ "x",
  .default = as.character(m)
)) %>% 
  mutate(r=case_when(
  r == 0 ~ " ",
  r > 0 ~ "x",
  .default = as.character(r)
)) %>% 
mutate(w=case_when(
  w == 0 ~ " ",
  w > 0 ~ "x",
  .default = as.character(w)
)) %>% 
  mutate(Guild=case_when(
  Guild == "r" ~ "roll",
  Guild == "t" ~ "tunnell",
  Guild == "d" ~ "dwell",
  .default = as.character(Guild)
)) %>% 
  rename(Species=species,
         N=n,
         Matrix=m,
         Corridor=c,
         Winged=w,
         Rectangular=r)
